\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-05-25 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
cleaning the paper adding some extra info

The set of test-cases that we are going to illustrate starts with an elementary case in a homogeneous domain. The aim of this test-case is to validate the different simulation/scenarios i.e., cross flow in a porous formation, evolution of fingers based on experimental Hele-Shaw work, behaviour of two-phase flow in more complicated formations and how factors like mobility ratio and heterogenities of the formations may affect the finger pattern.

Figure \ref{fig:simple_case} describes the starting point of the simulations that will follow. Fluid $1$ is from the left hand side of the formation. Later, different mobility ratios and different regions of various permeabilities will be introduced, but for now only few of these initial and boundary conditions will be applied. Boundary conditions will include a no-slip condition for the upper and lower boundary inlet is place at the left hand side while outlet on th right hand side of the domain. Initial conditions include initial values of velocity and pressure in the left and right hand side of the domain respectively. Also for different cases we have different geometrical domain aspect ratios, number of elements and types of grid (fixed and usntructured or adaptive and unstructured mesh).

%\noindent One more case to demonstrate the model validation against experiments is described in fig. \ref{fig:square}.
\noindent A square domain consisting of $4$ square regions in which each quarter is represented by a permeability value (Fig.\ref{fig:square}a) and $1$ value of different permeabilities (K is represented by the blue and red shaded square areas) as well as it is fully saturated with fluid $2$. At the upper and lower sides of the domain no-slip boundary condition is applied. The left hand side of the domain is defined as the inlet for fluid $1$ which is introduced along this side with a velocity of $u=1$. The right hand side is the outlet and pressure is set to $0$. Fluid $1$ across the left hand side of the domain is trying to displace the existing fluid $2$. What can been seen here is a cross flow case as the flow passes through different regions and evolves. The front start to collapse at the first half of the lenght D (D:distance) of the domain ($x= \frac{1}{2} D)$ (Fig.\ref{fig:square}b).

\noindent In this test-case above the two phase volume volume fractions have the same but opposite behaviours across the length of the formation. The velocity magnitute is built up starting from the inlet all the way to the middle of the square. There is a sharp pressure drop which is also an indication that the fluid $2$ cannot be displaced any further (see Fig.\ref{fig:square}) while the phase volume fraction is constant.

\medskip
A slightly modified test-case (see Fig.\ref{fig:testcase}) with similar initial and boundary conditions, but in this set of simulations the geometrical aspect ration is $2$. The model was also qualitatively validated against laboratory experiments conducted by \citet{evans_1994}. The last set of simulations as this is described in Fig.\ref{fig:1testcase} is and extension of the previous case and the aim of is to verify the behaviour of the flow for two different mobility ratios of $1$ and $10$ respectively.

>>>>

The set of test-cases that we are going to illustrate starts with an elementary case in a homogeneous domain. The aim of this test-case is to validate the different simulation/scenarios i.e., cross flow in a porous formation, evolution of fingers based on experimental Hele-Shaw work, behaviour of two-phase flow in more complicated formations and how factors like mobility ratio and heterogenities of the formations may affect the finger pattern. Figure \ref{fig:simple_case} describes the starting point of the simulations that will follow.

\medskip
Fluid $1$ is introduced from the left hand side of the formation. Later, different mobility ratios and different regions of various permeabilities will be introduced, but for now only few of these initial and boundary conditions will be applied. Boundary conditions will include a no-slip condition for the upper and lower boundary inlet is place at the left hand side while outlet on the right hand side of the domain. Initial conditions include initial values of velocity and pressure in the left and right hand side of the domain respectively. Also for different cases we have different geometrical domain aspect ratios, number of elements and types of grid (fixed and usntructured or adaptive and unstructured mesh will be used). 
%\noindent One more case to demonstrate the model validation against experiments is described in fig. \ref{fig:square}.
A domain consisting of $4$ square regions in which each quarter is represented by a permeability value (Fig.\ref{fig:square}a) and $1$ value of different permeabilities (K is represented by the blue and red shaded square areas) as well as it is fully saturated with fluid $2$. At the upper and lower sides of the domain no-slip boundary condition is applied. The left hand side of the domain is defined as the inlet for fluid $1$ which is introduced along this side with a velocity of $u=1$. The right hand side is the outlet and pressure is set to $0$. Fluid $1$ across the left hand side of the domain is trying to displace the existing fluid $2$. What can been seen here is a cross flow case as the flow passes through different regions and evolves. The front start to collapse at the first half of the lenght D (D:distance) of the domain ($x= \frac{1}{2} D)$ (Fig.\ref{fig:square}b).

\noindent In this test-case above the two phase volume volume fractions have the same but opposite behaviours across the length of the formation. The velocity magnitute is built up starting from the inlet all the way to the middle of the square. There is a sharp pressure drop which is also an indication that the fluid $2$ cannot be displaced any further %\ref{fig:square}) 
while the phase volume fraction is constant.

\medskip
A slightly modified test-case (see fig.\ref{fem_cv_represent_a}) 
with similar initial and boundary conditions, but in this set of simulations the geometrical aspect ration is $2$ is following. The model was also qualitatively validated against laboratory experiments conducted by \citet{evans_1994}. The last set of simulations as this is described in Fig.\ref{fig:1testcase} is and extension of the previous case and the aim of is to verify the behaviour of the flow for two different mobility ratios of $1$ and $10$ respectively.
